%    Copyright (C)  2015, Luca Fulchir<luca@fulchir.it>
%    Permission is granted to copy, distribute and/or modify this document
%    under the terms of the GNU Free Documentation License, Version 1.3
%    or any later version published by the Free Software Foundation;
%    with no Invariant Sections, no Front-Cover Texts, and no Back-Cover Texts.
%    A copy of the license is included in the section entitled "GNU
%    Free Documentation License".



\documentclass[11pt,a4paper]{refart}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{makeidx}
\usepackage{verbatimbox}
\usepackage{listings}
\usepackage{color}

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  basicstyle=\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygreen},    % comment style
  deletekeywords={...},            % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=single,                    % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\color{blue},       % keyword style
  language=C,                 % the language of the code
  %otherkeywords={*,...},            % if you want to add more keywords to the set
  %numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  %numbersep=5pt,                   % how far the line-numbers are from the code
  %numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{mymauve},     % string literal style
  tabsize=4,                       % sets default tabsize to 2 spaces
  title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
}

\title{Using libRaptorQ library}
\date{\today}
\makeindex

\begin{document}
\maketitle

\begin{abstract}

\textbf{libRaptorQ} is a C++11 implementation of the RaptorQ Forward Error Correction, as described in the \href{https://tools.ietf.org/html/rfc6330}{RFC6330} .

The implementation was started as a university laboratory project, and will be later used and included in \href{https://www.fenrirproject.org}{Fenrir}, the
maintainer's master thesis.

This implementation is quite short (the core is $\sim3k$ lines), thanks to the chosen language and the use of external libraries for matrix handling (eigen3).

libRaptorQ is the only RaptorQ implementation in C++, include C hooks, and it is the only free (\textbf{LGPL3}) implementation of the rfc, except for the (apache2)
java implementation, OpenRQ , which is much bigger ($\sim 46k$) and slower.
\end{abstract}

\vfill\hfill
\begin{verbbox}[\tiny]
Copyright (C)  2015, Luca Fulchir<luker@fenrirproject.org>
Permission is granted to copy, distribute and/or modify this document
under the terms of the GNU Free Documentation License, Version 1.3
or any later version published by the Free Software Foundation;
with no Invariant Sections, no Front-Cover Texts, and no Back-Cover Texts.
A copy of the license is included in the section entitled "GNU
Free Documentation License".
\end{verbbox}
\theverbbox

\newpage
\tableofcontents
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Contacts}\index{Contacts}

The main development and dicussions on the project, along with bug reporting, happens on
\href{https://www.fenrirproject.org/projects/libraptorq/}{the main website}.

\marginlabel{Mailing Lists} Mailing lists are available at \href{https://www.fenrirproject.org/lists}{https://www.fenrirproject.org/lists}\\
The two mailing lists are for development and announcments, but due to the low traffic of the development mailing list, it
can also be used by users for questions on the project.

\marginlabel{IRC} Since there are not many developers for now, the main irc channel is \textbf{\#fenrirproject} on freenode


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Build \& install}
\subsection{Get the source code}
Although things seems to work, no stable release has been released yet, as of \today.

This means you can only check this out with git.

To check out the repository:

\begin{verbatim}
$ git clone https://github.com/LucaFulchir/libRaptorQ.git
\end{verbatim}

You can also get it from our main server:

\begin{verbatim}
$ git clone https://www.fenrirproject.org/Luker/libRaptorQ.git
\end{verbatim}

\index{GPG}\marginlabel{GPG verification:}
Once you have cloned it, it's always a good thing to check the repository gpg
signatures, so you can import my key with:

\begin{verbatim}
$ gpg --keyserver pgp.mit.edu --recv-key D42DDF0A
\end{verbatim}

please check the full fingerprint, it should be this:

\begin{verbbox}[\footnotesize]
$ gpg2 --fingerprint D42DDF0A
 pub   rsa3072/D42DDF0A 2015-01-01 [expires: 2016-01-01]
       Key fingerprint = AB35 E45F 5CA5 E35B 8B55  818F 0157 D133 D42D DF0A
 uid       [ unknown] Luca Fulchir (2015 key) <luker@fenrirproject.org>
\end{verbbox}
\theverbbox
 

Now you have the source, and the key, it's enough to check the signature of the
last commit:

\begin{verbatim}
$ git log -n 1 --show-signature
\end{verbatim}

The important part is that you get something like this:

\begin{verbbox}[\footnotesize]
 gpg: Signature made Fri 27 Mar 2015 20:59:59 CET using RSA key ID D42DDF0A
 gpg: Good signature from "Luca Fulchir (2015 key) <luker@fenrirproject.org>"
 [unknown]
 gpg: WARNING: This key is not certified with a trusted signature!
 gpg:          There is no indication that the signature belongs to the owner.
 Primary key fingerprint: AB35 E45F 5CA5 E35B 8B55  818F 0157 D133 D42D DF0A
 Author: Luca Fulchir <luker@fenrirproject.org>
\end{verbbox}
\theverbbox

And as long as you got the right key, and you find the \textbf{"gpg: Good signature"} string,
you can be sure you have the right code.

\subsection{Dependencies}\index{dependencies}

libRaptorQ has only 2 dependencies:
\begin{description}
\item[\textbf{Eigen3}] This is used for matrix manipulation, which is a big part of RaptorQ.
\item[\textbf{git}] This is used not only to get the source, but also by the build system. We get the last git commit id and feed it to clang or gcc as seed for their
internal random number generator. This makes it possible to have reproducible builds.
\end{description}

\subsection{Build \& Install}

libRaptorQ uses the cMake build system, so things are fairly standard:

\begin{verbatim}
$ cd libRaptorQ.git
$ mkdir build
$ cmake ../
$ make -j 4
\end{verbatim}

By default, the libRaptorQ project tries to have deterministic builds. This means that if you compile things twice, or with two different computers, the
hash of the resulting library will be the same, provided that the same compiler (clang, gcc 4.8, gcc 4.9 etc) was used. Currently the only exception is the clang
compiler with the \textit{PROFILING} option enabled, and this will not likely be solved.

\index{cMake}
There are lots of options, you can use in cmake. As always, you can change them by adding ``\textbf{-Dcmake\_option=cmake\_value}'' when calling cmake.

You can always use the cmake-gui or ccmake commands to have the list of possible options.

The ones we recognize are:

\begin{description}
\item[LTO] yes/no. Default:\textbf{yes}. Enable \textit{Link Time Optimizatios} for clang or gcc. Makes libraries smaller and better optimized.
\item[PROFILING] yes/no. Default:\textbf{yes}. \textit{WARN: breaks deterministic builds with clang.}
Profiling compiles everything once, then runs a test to see which code paths are used more, and then
recompiles everything again, but making sure that the binary is optimized for those paths. Works with clang and gcc. Provides a slight speedup.
\item[CMAKE\_C\_COMPILER] gcc and clang are directly supported. other should work, too. This is only used if you want to build the C example.
\item[CMAKE\_CXX\_COMPILER] g++, clang++ are directly supported. other should work, too.
\item[STDLIB] change the c++ standard library. ``libstdc++'' for the (default) gcc one, ``libc++'' for the clang/llvm one. Note that it seems you can't use libc++ with gcc yet.
\item[CMAKE\_CXX\_FLAGS] Additional compiler flags you might want to pass.
\item[CMAKE\_BUILD\_TYPE] Type of build. you can choose between ``Debug'', ``Release'', ``MinSizeRel'' or ``RelWithDebInfo''
\item[CMAKE\_INSTALL\_PREFIX] Default to \textit{/usr/local}. Change it to fit your distribution guidelines.
\end{description}

Then you can build everything by running:
\begin{verbatim}
$ make -j 4
\end{verbatim}
Of course, you can configure the number of parallel jobs (the \textit{-j} parameter) to be what you need.

\marginlabel{Optional make targets:}
The following optional targets are also supported:
\begin{verbatim}
$ make docs tests examples
$ make everything
\end{verbatim}
The ``docs'' target builds this document, but you need latex with the refman style.
The tests are only useful to check perfromance of rfc compliance right now. ``examples'' compiles the C and C++ examples, which will not be installed.

\index{Install}\marginlabel{\textbf{Install:}}
The installation process is very simple:

\begin{verbatim}
$ make install DESTDIR=...
\end{verbatim}

You can change the \textit{DESTDIR} parameter to fit your distribution guidelines.

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Working with RaptorQ}
\subsection{Theory (you really need this)}\index{Theory}

To be able to work with liRaptorQ, you must first understand how the RaptorQ algorithms works. We won't go into the details, but just what you need
to be able to tune the algorithm to your needs.


\marginlabel{Fountain codes:}
Fountain codes are a special \textit{Forward-Error-Correcting} code class, which characteristic is simple: if you want to send $K$ packets, you actually
send $K+X$ packets, and the receiver only needs to get any $K$ packets to be able to reconstruct your data. The number $X$ of overhead packets can be as big
as you need (theoretically infinite), so you can tune it to be slightly higher than the expected packet loss.

\marginlabel{Systematic codes:} RaptorQ is also a systematic code. This means that those first $K$ packets are the input \textit{as-is} (\textbf{source symbols}),
and the $X$ packets (\textbf{repair symbols}) have the information needed to recover any of the lost source packets. This has the big advantage of
avoiding any kind of time and memory consuming decoding if there is no packet loss during the transmission.

\marginlabel{Complexity:} The RaptorQ algorithm is often presented as having a linear time encoder and decoder. This is both false and misleading.
Generating the source or repair symbols from the intermediate symbols has linear complexity. Generating the intermediate symbols has cubic complexity on the
number of symbols. Which is a completely different thing.
It is still very quick. On a core i7, 2.4Ghz, you need to wait \textit{0.4ms} for $10$ symbols, \textit{280ms} for 1.000 symbols, but it can take an hour for $27.000$ symbols.
RaptorQ handles up to $56.403$ symbols.

\subsection{Blocks \& Symbols}

To understand how to properly use and tune libRaptorQ, you first need to understand how RaptorQ handles its inputs, outputs, and what the time and memory
constraints are.

\index{Sequencing}\marginlabel{Input sequencing:}
RaptorQ needs to have the whole input you want to send before it can start working.\\
This means that it might be a little more difficult to use in live-streaming contexts, or where you need real-time data, but libRaptorQ will have options to
facilitate usage even in those contexts.

Once you have the whole input, RaptorQ divides it into \textbf{blocks}. Each block \textit{is encoded and decoded independently} and will be divided into \textbf{symbols}. Each symbol \textit{should}
be transmitted separately in its own packet (if you are on the network).

\index{Sequencing!Sizes}\marginlabel{Sizes:}Each input can have up to \textit{256 blocks}, each block can have up to \textit{$56.403$ symbols}, and each
symbol can have up to \textit{$2^{16}-1$ bytes}long. This gives a maximum files size of almost $881$ GB (946270874880 bytes to be exact)

\index{Interleaving}\marginlabel{Interleaving:}
An other feature of RaptorQ is to automatically provide some interleaving of the input data before transmitting it. This means that one symbol will not
represent one sequential chunk of your input data, but more likely it's the concatenation of different \textbf{sub-symbols}. The size of the subsymbol must thus
be a fraction of the symbol size. This feature is not used if you set the size of the subsymbol to the size of symbol.


\marginlabel{Memory and Time:}
Memory and time requirements are to be considered, though, as RaptorQ needs to run a cubic algorithm on matrix of size $K*K$, where $K$ is the number of
symbols in each block.\\
The algorithm needs to keep in memory two of these matrices, although most of the work is done on only one.\\
This is actually a lot. More benchmarks and optimizations will come later, for now remember that with 10 symbols it takes something like 0.4ms on a core i7 2.4GHZ, 280ms with 1000 symbols, and up to an hour with 27.000 symbols.


\subsection{C++ interface}
\index{Interface!C++}
To use the C++ interface you only need to include the \textbf{RaptorQ.hpp} header, and link \textbf{libRaptorQ} and your threading library (usually
\textit{libpthread}).

To provide grater flexibility, the whole library uses iterators to read your data, and to write the data onto your data structures.\\
This means that a big part of the library is a template, which adapts to the alignment of the data in the data structures you use.

\index{Iterators}\marginlabel{Templates}
There are two main classes you will use:
\begin{verbatim}
template <typename Rnd_It, typename Fwd_It>
class Encoder

template <typename In_It, typename Fwd_It>
class Decoder
\end{verbatim}

As you might guess, the classes for the encoder and decoder take two template parameters.\\
For the \textbf{Encoder}, the first parameter \textit{MUST} be a \textit{random access iterator} to the input data, and the second parameter is an
\textit{forward iterator}. The random access iterator will be used to scan your input data, and perform an interleaving (if you did not set the same size the
symbol and to the subsymbol). The forward iterator will be used to write the data to your structure.\\
The same is done for the \textbf{Decoder}, but we do not need to do any interleaving on the input, so the first iterator can be just an input iterator,
and nothing more.


\subsubsection{The Encoder}
\index{Encoder!C++}
You can instantiate an encoder for example by doing:

\begin{lstlisting}[language=C++]
std::vector<uint32_t> input, output;
...
using T_it = typename std::vector<uint32_t>::iterator;
RaptorQ::Encoder<T_it, T_it> enc (input.begin(),
                                  input.end(),
                                  4, 1444, 10000)
\end{lstlisting}

This will create an Encoder that works on vectors of unsigned 32 bit integers for both input and output, that will create symbols of size 1444 bytes, interleaving
your input every 4 bytes, and try to work with big number of symbols per blocks (\textbf{TODO: explain memory requirements})

The available methods for the encoder are the following:

\begin{description}
\item[operator bool()] \textbf{return:bool}\\
False if constructor parameters did not make sense. Else true.

\item[OTI\_Common()] \textbf{return: OTI\_Common\_Data}, aka \textit{uint64\_t}.\\
Keeps total \textbf{file size and symbol size}. You need to send this to the receiver, so that it will be able to properly decode the data.

\item[OTI\_Scheme\_Specific\_Data()] \textbf{return: OTI\_Scheme\_Specific\_Data}, aka \textit{uint32\_t}.\\
Keeps number of \textbf{source blocks, sub blocks, and alignment}. As for the OTI\_Common\_Data, you need to send this to the receiver to be able to
properly decode the data.

\item[encode] \textbf{Input: Fwd\_It \&output, const Fwd\_It end, const uint32\_t esi, const uint8\_t sbn}.\\
\textbf{return:uint64\_t}.\\
Take as input the iterators to the data structure into where we have to save the encoded data, the \textbf{Encoding Symbol Id} and the
\textbf{Source Block Number}. As you are writing in C++, you probably want to use the iterators begin/end, though. Returns the number of written
iterators (\textbf{NOT} the bytes)

\item[encode] \textbf{Input: Fwd\_It \&output, const Fwd\_It end, const uint32\_t id}.\\
\textbf{return:uint64\_t}.\\
Exactly as before, but the \textbf{id} contains both the \textit{source block number} and the \textit{encoding symbol id}

\item[begin()] \textbf{return: Block\_Iterator<Rnd\_It, Fwd\_It>}\\
This returns an iterator to the blocks in which RaptorQ divided the input data. See later to understand how to use it.
\item[end()] \textbf{return: const Block\_Iterator<Rnd\_It, Fwd\_It>}\\
This returns an iterator to the end of the blocks in which RaptorQ divided the input data. See later to understand how to use it.

\item[precompute] \textbf{Input:const uint8\_t threads, const bool background}\\
\textbf{return: void}\\
Do the work of computing all different blocks in multithread. If \textit{background} is true, then return immediately, else return only when the job is done.\\
If \textit{threads} is $0$, try to guess the maximum threads from the number of available cpus.

\item [precompute\_max\_memory] \textbf{return: size\_t}\\
Each precomputation can take a lot of memory, depending on the configuration, so you might want to limit the number of precomputations run in parallel
depending on the memory used. This method returns the amount of memory taken by \textbf{ONE} precomputation.

\item [free] \textbf{Input: const uint8\_t sbn)}\\
\textbf{return: void}\\
Each block takes some memory, (a bit more than $symbols * symbol_size$), so once you are done sending source and repair symbols for one block,
you might want to free the memory of that block.

\item[blocks()] \textbf{return: uint8\_t} The number of blocks.

\item[block\_size()] \textbf{Input: const uint8\_t sbn}\\
\textbf{return: uint32\_t}\\
The block size, in bytes. Each block can have different symbols and thus different size.

\item[symbol\_size()] \textbf{return: uint16\_t} The size of a symbol.

\item[symbols] \textbf{Input:uint8\_t sbn}\\
\textbf{return: uint16\_t}\\
The number of symbols in a specific block. different blocks can have different symbols.

\item[max\_repair] \textbf{Input: const uint8\_t sbn)}\\
\textbf{return: uint32\_t}\\
The maximum amount of repair symbols that you can generate. Something less than $2^{24}$, but the exact number depends on the number of symbols
in a block
\end{description}

~\\

\subsubsection{Blocks}
\index{Blocks!C++}
With the \textit{begin()/end()} calls you get \textit{Input iterators} to the blocks. a Block is has the following type:
\begin{lstlisting}[language=C++]
template <typename Rnd_It, typename Fwd_It>
class Block
\end{lstlisting}

and exposes the 4 following methods:
\begin{description}
\item[begin\_source]\textbf{return: Symbol\_Iterator}
\item[end\_source]\textbf{return: Symbol\_Iterator}
\item[begin\_repair]\textbf{return: Symbol\_Iterator}
\item[end\_repair]\textbf{Input: const uint32\_t max\_repair}\\
\textbf{return: Symbol\_Iterator}
\item[max\_repair]\textbf{return:uint32\_t}
\item[symbols]\textbf{return: uint16\_t}
\item[block\_size]\textbf{return: uint32\_t}
\end{description}

As the names explain, you will get an iterator to the symbols in the block. As the number of repair symbols can vary, for now you get two separate begin/ends,
so that you can check when you sent the source symbols, and how many repair symbols you send.\\
The other functions are helpers for the details of the block.


\subsubsection{Symbols}
\index{Symbols!C++}
Finally, through the \textit{Symbol\_Iterator} \textit{Input Iterator} we get the \textbf{Symbol} class:
\begin{lstlisting}[language=C++]
template <typename Rnd_It, typename Fwd_It>
class Symbol
\end{lstlisting}

which exposes the 2 methods we need to get the symbol data:

\begin{description}
\item[operator*]\textbf{Input:Fwd\_It \&start, const Fwd\_It end}\\
\textbf{return: uint64\_t}\\
takes a forward iterator, and fill it with the symbol data. returns the number of written iterators.
\item[id()]\textbf{return: uint32\_t}\\
return the id (\textit{$sbn + esi$}) of this symbol, that you need to include in every packet you send, before the symbols.
\end{description}

\subsubsection{The Decoder}
\index{Decoder!C++}

The decoder is a bit simpler than the encoder.

Theere are two constructors for the Decoder:

\begin{lstlisting}[language=C++]
 std::vector<uint32_t> input, output;
 using T_it = typename std::vector<uint32_t>::iterator;
 RaptorQ::Decoder<T_it, T_it> dec (
                 const OTI_Common_Data common,
                 const OTI_Scheme_Specific_Data scheme)
                              
 RaptorQ::Decoder<T_it, T_it> dec (uint64_t size,
                                  uint16_t symbol_size,
                                  uint16_t sub_blocks,
                                  uint8_t blocks)
\end{lstlisting}

Which should be pretty self-explanatory, once you understand how the encoder works.

The remaining methods are:
\begin{description}
\item[decode]\textbf{Input: Fwd\_It \&start, const Fwd\_It end}\\
\textbf{return:uint64\_t}\\
Write \textbf{all} the blocks into the iterator. refuses to write if the input has not been completely received. Return the number of iterators written.

\item[decode]\textbf{Input: Fwd\_It \&start, const Fwd\_It end, const uint8\_t sbn}\\
\textbf{return:uint64\_t}\\
Write a specific block into the iterator. Refuses to write if the input for that block has not been completely received.

\item[add\_symbol]\textbf{In\_It \&start, const In\_It end, const uint32\_t esi, const uint8\_t sbn}\\
\textbf{return: bool}\\
Add one symbol, while explicitly specifying the symbol id and the block id.

\item[add\_symbol]\textbf{In\_It \&start, const In\_It end, const uint32\_t id}\\
\textbf{return: bool}\\
Same as before, but extract the block id and the symbol id from the \textit{id} parameter

\item[free]\textbf{Input: const uint8\_t sbn}\\
\textbf{return: void}\\
You might have stopped using a block, but the memory is still there. free it.

\item[blocks()] \textbf{return: uint8\_t} The number of blocks.

\item[block\_size()] \textbf{Input: const uint8\_t sbn}\\
\textbf{return: uint32\_t}\\
The block size, in bytes. Each block can have different symbols and thus different size.

\item[symbol\_size()] \textbf{return: uint16\_t} The size of a symbol.

\item[symbols] \textbf{Input:uint8\_t sbn}\\
\textbf{return: uint16\_t}\\
The number of symbols in a specific block. different blocks can have different symbols.
\end{description}
\newpage

\subsection{C interface}\index{Interface!C}
The C interface looks a lot like the C++ one.\\
You need to include the \textbf{cRaptorQ.h} header, and link the \textit{libRaptorQ} library.\\
\marginlabel{Static linking}\index{Static Linking}
If you are working with the static version of libRaptorQ remember to link the C++ standard library used when
compiling the library (\textit{libstdc++} for gcc or maybe \textit{libc++} for clang), your threding library (usually \textit{libpthread}), and the C math library (\textit{libm}).\\

First of all, you need to build the encoder or the decoder.

The C interface is just a wrapper around the C++ code, so you still have to specify the same things as before.
A quick glance at the constructors should give you all the information you need:

\marginlabel{C Constructors}
\begin{lstlisting}[language=C]
typedef enum { NONE = 0,
         ENC_8 = 1, ENC_16 = 2, ENC_32 = 3, ENC_64 = 4,
         DEC_8 = 5, DEC_16 = 6, DEC_32 = 7, DEC_64 = 8}
              RaptorQ_type;

struct RAPTORQ_LOCAL RaptorQ_ptr
{
  void *ptr = nullptr;
  const RaptorQ_type type;
};

RaptorQ_ptr* RaptorQ_Enc (const RaptorQ_type type,
                    void *data,
                    const uint64_t size,
                    const uint16_t min_subsymbol_size,
                    const uint16_t symbol_size,
                    const size_t max_memory);

RaptorQ_ptr* RaptorQ_Dec (const RaptorQ_type type,
              const RaptorQ_OTI_Common_Data common,
              const RaptorQ_OTI_Scheme_Specific_Data
                                                scheme);
\end{lstlisting}

The encoder and decoder must have a specific alignment. in C++ you can also have different
alignments for the input and output, while in C things are a bit more strict as we have to enumerate
all the possible cases. So you only get the same data alignment for both input and output.\\
Still, you don't lose anything in performance.\\

\newpage

\subsubsection{Common functions for (de/en)coding}

These functions are used by both the decoder and the decoder, and will be helpful in tracking how much memory
you will need to allocate, or in general in managing the encoder and decoder.

The \textbf{ptr} must be a valid encoder or decoder.
The names for now are self-explanatory. Blocks can have different symbols, so the size of a block and the number of symbols in a block
depend on which block we are talking about.

\marginlabel{symbols, blocks, memory}
\begin{lstlisting}[language=C]
uint16_t RaptorQ_symbol_size (struct RaptorQ_ptr *ptr);
uint8_t RaptorQ_blocks (struct RaptorQ_ptr *ptr);
uint32_t RaptorQ_block_size (struct RaptorQ_ptr *ptr,
                                    const uint8_t sbn);
uint16_t RaptorQ_symbols (struct RaptorQ_ptr *ptr,
                                    const uint8_t sbn);

void RaptorQ_free (struct RaptorQ_ptr **ptr);
void RaptorQ_free_block (struct RaptorQ_ptr *ptr,
                                    const uint8_t sbn);
\end{lstlisting}
Finally, when you are done working with a block, you can free the memory associated with the single block
and just free the whole (en/de)coder when you are done. Freeing the whole (en/de)coder will obviously free
also all the blocks.


\newpage
\subsubsection{Encoding}

\marginlabel{OTI Data}
First, we need to tell the receiver all the parameters that the encoder is using, and for that two functions are provided:

\begin{lstlisting}[language=C]
typedef uint64_t RaptorQ_OTI_Common_Data;
typedef uint32_t RaptorQ_OTI_Scheme_Specific_Data;

RaptorQ_OTI_Common_Data RaptorQ_OTI_Common (
                               struct RaptorQ_ptr *enc);
RaptorQ_OTI_Scheme_Specific_Data RaptorQ_OTI_Scheme (
                               struct RaptorQ_ptr *enc);
\end{lstlisting}

\index{Encoder!C}\marginlabel{Encoding}

\begin{lstlisting}[language=C]
// maximum number of repair symbol in a block
uint32_t RaptorQ_max_repair (RaptorQ_ptr *enc,
                                   const uint8_t sbn);
//estimate bytes of ram used in the precomputation
// of one block
size_t RaptorQ_precompute_max_memory (
                               struct RaptorQ_ptr *enc);
// do the precomputation.
void RaptorQ_precompute (struct RaptorQ_ptr *enc,
                                 const uint8_t threads,
                                 const bool background);

// encode one symbol. source block number and
// symbol id are in the ``id'' field.
// returns number of alignments written.
uint64_t RaptorQ_encode_id (struct RaptorQ_ptr *enc,
                                  void **data,
                                  const uint64_t size,
                                  const uint32_t id);
// encode one symbol. same as before
uint64_t RaptorQ_encode (struct RaptorQ_ptr *enc,
                                  void **data,
                                  const uint64_t size,
                                  const uint32_t esi,
                                  const uint8_t sbn);
// build an ``id'' field out of an esi and sbn field.
uint32_t RaptorQ_id (const uint32_t esi,
                                  const uint8_t sbn);
\end{lstlisting}
As for the C++ version, everything is thread-safe.

You can start the precomputation in background and not worry about it.\\
If you request repair symbols before the computation is finished, the call will block until the data is available.

The \textbf{encode} functions are the same, and will encode \textbf{one} symbol.
They work for both source symbols and repair symbols, just keep increasing the \textit{esi} field


\newpage
\subsubsection{Decoding}
\index{Decoder!C}\marginlabel{Decoding}
\begin{lstlisting}[language=C]
// return the total size of the data that will be
// decoded
uint64_t RaptorQ_bytes (struct RaptorQ_ptr *dec);

// decode all blocks.
// returns the number of written alignments.
// returns 0 if decoding of *everything* is not possible
uint64_t RaptorQ_decode (struct RaptorQ_ptr *dec,
                                   void **data,
                                   const size_t size);
// decode only one block (if possible)
// returns 0 if decoding of the block is not possible.
uint64_t RaptorQ_decode_block (struct RaptorQ_ptr *dec,
                                   void **data,
                                   const size_t size,
                                   const uint8_t sbn);

// add a received symbol to the structure.
// either by using the `id' field
bool RaptorQ_add_symbol_id (struct RaptorQ_ptr *dec,
                                   void **data,
                                   const uint32_t size,
                                   const uint32_t id);
// or by explicitely declaring esi and sbn
bool RaptorQ_add_symbol (struct RaptorQ_ptr *dec,
                                   void **data,
                                   const uint32_t size,
                                   const uint32_t esi,
                                   const uint8_t sbn);
\end{lstlisting}



\input{GNU_FDL.tex}

\printindex
\end{document}
